%-------------------------
% Resume in Latex
% Original Author : Sourabh Bajaj
% Modified by : Benson Chau
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://benschau.com/}{\Large Benson Chau}} & Email : \href{mailto:ben.chau@gatech.edu}{ben.chau@gatech.edu}\\
  \href{https://benschau.com/}{https://www.benschau.com} & Mobile : +1-404-434-5548 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Bachelor of Science in Computer Science;  GPA: 3.48}{Aug. 2017 -- May 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

	\resumeSubheading
	  {Georgia Tech Research Institute}{Atlanta, GA}
	  {ICL Research Assistant and CIPHER Hardware Security Intern}{Nov 2018 -- Current}
	  \resumeItemListStart
	  		  	   
	  	\resumeItem{CIPHER - Hardware Security Intern}
	  	   {Constructing a heterogeneous multi-chip emulator; developing an application built to help analysts understand and manipulate hardware designs.}
	  	
        \resumeItem{CIPHER - JIT Compiler Benchmarking}
	  	   {Created a JIT benchmarking suite that utilizes several handwritten LLVM and Cranelift programs to show their performance differences.}

        \resumeItem{CIPHER - Open Source Contributing}
           {Added a patch to the Cranelift JIT compiler to prevent unauthorized memory accesses in security-enhanced Linux distributions using anonymous memory maps.}
	  
	  	\resumeItem{ICL - Research Assistant}
	  	   {Examining the capabilities of new RTX ray-tracing technology against the current state-of-the-art in the context of radio frequency signals in urban areas; created a pipeline for creating sample data and an OpenGL visualizer for CPU-based rendering, assisted in the development of a NVIDIA OptiX raytracer.}

	  \resumeItemListEnd

    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {PACE HPC Intern and ACL Resarch Assistant}{May 2018 -- Nov 2018}
      \resumeItemListStart
        \resumeItem{PACE - Lead Student Assistant}
          {Managed a team of student assistants in maintaining and building software for the computing cluster.}
        \resumeItem{PACE - Automation Scripting}
          {Developed bash scripts to automate building specific package configurations and to sync against remote repositories.}
        \resumeItem{ACL - Research Assistant}
          {Created an automated benchmarking suite for several types of neural networks against popular datasets.}
        \resumeItem{ACL - BitFusion}
          {Co-authored the BitFusion ISA paper (ISCA 2018) describing a dynamically composable architecture for neural network acceleration.}
        \resumeItem{Smart City Infrastructure}
          {Identified vehicles using background subtraction and feature detection techniques to analyze driver behavior near high density traffic and safety devices.}
        \resumeItem{Automated Algorithm Design} 
          {Maintained the caching feature of the genetic programming engine EMADE; developed a documentation standard and several bug fixes.}
      \resumeItemListEnd
      
    \resumeSubheading
      {University of Georgia Small Satellite Lab}{Athens, GA}
      {Algorithm Developer and Student Researcher}{Summer 2017}
      \resumeItemListStart
        \resumeItem{Algorithm Developer}
          {Assembled a prototype structure from motion pipeline for 3D reconstruction processing on a CubeSat embedded system.}
        \resumeItem{Student Researcher}
          {Wrote a trade study on the practicality of structure from motion libraries for use on a CubeSat regarding computational complexity and design.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{CHIP8 Emulator}
      {Open source CHIP8 emulator created in Rust as an introductory hardware project.}
    % \resumeSubItem{ATMega128 Emulator}
    %  {An emulator for the AVR's Harvard architecture and ATMega128 specific hardware.}
    \resumeSubItem{EsoInterpreters}
      {Implementations of esoteric compilers written in Rust with custom JIT compilation.}
    \resumeSubItem{rsh and cpp-sh}
      {Open source Linux shell with background/foreground process management, job control, and text parsing.}
    \resumeSubItem{SimpleNets}
      {A repository of neural network structures written in Python; implemented an RNN that samples text from Don Quixote.}
    \resumeSubItem{Verilog Processor}
      {A pipelined processor with programmable interrupt handlers written in Verilog for an Altera DE-0 FPGA.}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
